Analysis

### 2019-11-29 analysis-cfa.Rmd
update2911

---
title: "Analysis"
date: "29-11-2019"
output: 
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
---

@@

# Version 01:

@@

fit1 <- cfa(model = model01,data = dat01)

summary(fit1,standardized=TRUE, fit.measures=TRUE)

semPlot::semPaths(object = fit1,what = "std")
```

# Version 02:

@@

fit2 <- cfa(model = model02,data = dat02)

summary(fit2,standardized=TRUE, fit.measures=TRUE)

semPlot::semPaths(object = fit2,what = "std")
```

# Version 03: batería orden aleatorio

@@

fit3 <- cfa(model = model03,data = dat03)

summary(fit3,standardized=TRUE, fit.measures=TRUE)

semPlot::semPaths(object = fit3,what = "std")
```

# Version 04:  Modelo muestra completa

@@

fit4 <- cfa(model = model04,data = dat04)

summary(fit4,standardized=TRUE, fit.measures=TRUE)

semPlot::semPaths(object = fit4,what = "std")
```

>>>>

---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
---

# Análisis PPM-S

@@

## Version 01:

@@

fit1 <- cfa(model = model01,data = dat01,ordered = c("meritv01_perc_effort","meritv01_perc_talent",
                                                     "meritv01_perc_wpart","meritv01_perc_netw",
                                                     "meritv01_pref_effort","meritv01_pref_talent",
                                                     "meritv01_pref_wpart","meritv01_pref_netw"))

summary(fit1,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit1,what = "std",thresholds = FALSE, intercepts = FALSE)
```

## Version 02:

@@

fit2 <- cfa(model = model02,data = dat02,ordered = c("meritv02_perc_effort","meritv02_perc_talent",
                                                     "meritv02_perc_wpart","meritv02_perc_netw",
                                                     "meritv02_pref_effort","meritv02_pref_talent",
                                                     "meritv02_pref_wpart","meritv02_pref_netw"))

summary(fit2,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit2,what = "std")
```

## Version 03: orden aleatorio

@@

fit3 <- cfa(model = model03,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                     "meritv03_perc_wpart","meritv03_perc_netw",
                                                     "meritv03_pref_effort","meritv03_pref_talent",
                                                     "meritv03_pref_wpart","meritv03_pref_netw"))

summary(fit3,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit3,what = "std",thresholds = FALSE, intercepts = FALSE)
```

## Version 04: muestra completa

@@

fit4 <- cfa(model = model04,data = dat04)
summary(fit4,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit4,what = "std",thresholds = FALSE, intercepts = FALSE)
```
